DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-01 ase2017/paper.tex
specified the DSSynth back-end used for the experiments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
typo + question

\newcommand\tool{{DSSynth Toolbox}\xspace}
\newcommand{\fwl}[1]{\mathcal{FWL}[#1]}

@@

For all evaluated benchmarks, the signal input range related to the control system 
lies between $-1$ and $1$. The implementation features used for digital controller are:
$8$-bits for the integer part (including the sign bit) and $8$-bits for the fractional 
part. All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle 
Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.

@@

For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
for our set of benchmarks represented by transfer functions or state-space equations. 
We employed a diverse set of real-world benchmarks extracted from the control literature. 
However, note that this set of benchmarks is still limited within the scope of this paper, and 
the performance may not be generalized to other benchmarks. 
The media runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
for transfer functions, the average synthesis time amounts to $123.6$\,s.

>>>>

\renewcommand{\baselinestretch}{0.991}
\newcommand\tool{{DSSynth Toolbox}\xspace}
\newcommand{\fwl}[1]{\mathcal{FWL}[#1]}

@@

For all evaluated benchmarks, the signal input range related to the control system 
lies between $-1$ and $1$. The implementation features used for digital controller are:
$8$-bits for the integer part (including the sign bit) and $8$-bits for the fractional 
part. We have run the \tool using the CEGIS with multi-staged verification (cf.~Section~\ref{sec:CEGIS}).
All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle 
Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.

@@

\textcolor{red}{Why are the experiments only mentioning stable controllers? Up until this point, we discuss stable and safe controllers.}

For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
for our set of benchmarks represented by transfer functions or state-space equations. 
We employed a diverse set of real-world benchmarks extracted from the control literature. 
However, note that this set of benchmarks is still limited within the scope of this paper, and 
the performance may not be generalized to other benchmarks. 
The median runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
for transfer functions, the average synthesis time amounts to $123.6$\,s.
